### 2017-01-15 sec-results.tex
Add experiment results for mean rank with 2 -> 2 transition ranking.

To quantify this finding, we perform the following experiment. First, we
select all students from \textretrieval{} who completed all of the quizzes
$\mathbf{L}_q \subset \mathbf{L}$. This gives us 1,985 students along with
their average quiz score. We then create a ranked list of the students in
$\mathbf{L}_q$ by sorting them by their ``preference'' for a specific
latent state
\begin{equation}
  p_\ell(i) = \frac{\sum_{t=1}^T \gamma_t^{(\mathbf{o}_\ell)}(i)}
  {\sum_{j=1}^{K} \sum_{t=1}^T \gamma_t^{(\mathbf{o}_\ell)}(j)}
\end{equation}
where $\mathbf{o}_\ell$ is the list of action sequences for student $\ell$
and $\gamma$ is defined as before and computed using the Baum-Welch
algorithm. We can now compare the average rank in this list for both
the ``perfect'' student group and the ``low'' student group: a useful state
for distinguishing the two groups should result in a ranked list with
statistically significant differences in average rank between the two
groups. Our results are summarized in Table~\ref{table:mean-rank}. Indeed,
we discover that states 1 and 2 are useful for teasing apart these two
groups: state 1 ranks students in the ``low'' group significantly higher
than those in the ``perfect'' group, and state 2 does the opposite and
prefers students in the ``perfect'' group to those in the ``low'' group.

\begin{table}
  \centering
  \begin{tabular}{r|rrrr}
    \textbf{Group} & \textbf{State 0} & \textbf{State 1}^\dagger &
    \textbf{State 2}^\dagger & \textbf{State 3}\\\hline
    \textbf{Perfect} & 975.3  & 1001.5 & 999.0  & 1056.5\\
    \textbf{Low}     & 1024.9 & 816.4  & 1230.5 & 1161.2\\
  \end{tabular}
  \caption{Average rank for ``perfect'' and ``low'' student groups in the
  ranked lists associated with the four latent states found by a TL-HMM.
  $\dagger$ indicates statistically significant different mean ranks at $p
  < 0.01$ according to an unpaired $t$-test.}
  \label{table:mean-rank}
\end{table}

>>>>

\begin{table}
  \centering
  \begin{tabular}{r|rrrrr}
    \textbf{Group} & \textbf{State 0} & \textbf{State 1}^\dagger &
    \textbf{State 2}^\dagger & \textbf{State 3} & \textbf{State 2
    $\rightarrow$ 2}^\dagger\\\hline
    \textbf{Perfect} & 975.3  & 1001.5 & 999.0  & 1056.5 & 939.6\\
    \textbf{Low}     & 1024.9 & 816.4  & 1230.5 & 1161.2 & 1187.4\\
  \end{tabular}
  \caption{Average rank for ``perfect'' and ``low'' student groups in the
  ranked lists associated with the four latent states found by a TL-HMM.
  $\dagger$ indicates statistically significant different mean ranks at $p
  < 0.01$ according to an unpaired $t$-test.}
  \label{table:mean-rank}
\end{table}

To quantify this finding, we perform the following experiment. First, we
select all students from \textretrieval{} who completed all of the quizzes
$\mathbf{L}_q \subset \mathbf{L}$. This gives us 1,985 students along with
their average quiz score. We then create a ranked list of the students in
$\mathbf{L}_q$ by sorting them by their ``preference'' for a specific
latent state
\begin{equation}
  p_\ell(i) = \frac{\sum_{t=1}^T \gamma_t^{(\mathbf{o}_\ell)}(i)}
  {\sum_{j=1}^{K} \sum_{t=1}^T \gamma_t^{(\mathbf{o}_\ell)}(j)}
\end{equation}
where $\mathbf{o}_\ell$ is the list of action sequences for student $\ell$
and $\gamma$ is defined as before and computed using the Baum-Welch
algorithm. We can now compare the average rank in this list for both
the ``perfect'' student group and the ``low'' student group: a useful state
for distinguishing the two groups should result in a ranked list with
statistically significant differences in average rank between the two
groups. Our results are summarized in Table~\ref{table:mean-rank}. Indeed,
we discover that states 1 and 2 are correlated with the ``perfect'' or
``low'' groups: state 1 ranks students in the ``low'' group significantly higher
than those in the ``perfect'' group, and state 2 does the opposite and
prefers students in the ``perfect'' group to those in the ``low'' group.

Returning to Figure~\ref{fig:trans-comp}, we an also see a difference in
the transitions between the latent states. In particular, look at the
transitions in Figure~\ref{fig:trans-perfect} and
Figure~\ref{fig:trans-low} that leave state 2. In the ``perfect'' group,
nearly all of this probability mass is allocated for the self-loop ($p
\approx 0.93$). In the ``low'' group, this self loop is less strong ($p
\approx 0.80$; most easily seen by noting that the edges leaving state 2
are darker than for the ``perfect'' group). We can perform a similar
experiment to above by producing a ranked list of students $\ell \in
\mathbf{L}_q$ by their staying probability for state 2 (that is, given that
a student $\ell$ is already in state 2, how likely are they to remain there
in the next action sequence?). This can be computed as
\begin{equation}
  p_\ell(2, 2) = \frac{\sum_{t=1}^{T-1} \xi_t^{(\mathbf{o}_\ell)}(2,2)}
  {\sum_{i=1}^K \sum_{t=1}^{T-1} \xi_t^{(\mathbf{o}_\ell)}(2,i)}
\end{equation}
where $\xi$ is defined as before and computed using the Baum-Welch
algorithm. The last column of Table~\ref{table:mean-rank} indicates that
this transition feature also correlates with the achievement group and
results in significant differences in mean rank.
